### Question 0

*  Draw a concepts diagram that uses all the following Github terminology 
   * Include any missing keywords that will simplify the concepts diagrams 


`Push`, `Repository`, `Clone`, `Pull`, `Pull Request`, `Branch`, `Merging`, `Github Client`, `README file`, `Private or Public`

https://drive.google.com/file/d/16NQogNJbMLFBp2jfbwQBSjqcslz6L4oi/view?usp=sharing

#### Question 1

`matrix(c(1,2,3,4,5,6) , nrow = 3)`

* Running the expression produces the following matrix

|  |  |
|---|---|
| 1 | 4 |
| 2 | 5 |
| 3 | 6 |

* How can you modify the call to `matrix()` to produce the following matrix instead?

|   | col_1 |  col_2 |
| --- |---|---|
| row_1 | 1 | 2 |
| row_2 | 3 | 4 |
| row_3 | 5 | 6 |

* Note that you need to name the columns (col_1 and col_2) and name the rows (row_1, row_2, row_3)

Hint: Use the `?` symbol to invoke the matrix documentation

```{r}
rownames <- c("row_1", "row_2", "row_3")
colnames <- c("col_1", "col_2")
matrix(c(1,2,3,4,5,6) , nrow = 3, byrow = TRUE, dimnames = list(rownames, colnames ))
```

#### Question 1

`matrix(c(1,2,3,4,5,6) , nrow = 3)`

* Running the expression produces the following matrix

|  |  |
|---|---|
| 1 | 4 |
| 2 | 5 |
| 3 | 6 |

* How can you modify the call to `matrix()` to produce the following matrix instead?

|   | col_1 |  col_2 |
| --- |---|---|
| row_1 | 1 | 2 |
| row_2 | 3 | 4 |
| row_3 | 5 | 6 |

* Note that you need to name the columns (col_1 and col_2) and name the rows (row_1, row_2, row_3)

Hint: Use the `?` symbol to invoke the matrix documentation

```{r}
rownames <- c("row_1", "row_2", "row_3")
colnames <- c("col_1", "col_2")
matrix(c(1,2,3,4,5,6) , nrow = 3, byrow = TRUE, dimnames = list(rownames, colnames ))
```

#### Question 2

* Load then sort the airquality data frame on its `Temp` and `Solar.R` columns in reverse order (largest to smallest values)
  * The function to sort a data frame is called order
* Display only the first 15 lines of your table

```{r}
data(airquality)
```


```{r}
sorted_airquality <- airquality[order(-airquality$Temp, -airquality$Solar.R), ]

head(sorted_airquality, 15)
```






#### Question 3

* Sort the airquality data frame on its `Temp` in decreasing order and `Solar.R` in increasing order
* Display only the first 15 lines of your table

```{r}
sorted_airquality2 <- airquality[order(-airquality$Temp, airquality$Solar.R), ]

head(sorted_airquality, 15)
```

#### Question 4

* There are various ways to select a subset of observations from a data frame.

* Consult your [R Reference Card](https://cran.r-project.org/doc/contrib/Baggott-refcard-v2.pdf), see `Data Selection and Manipulation` section.
  * What operations can you use to select all observations where the temperature is 72. Give at least two different answers to this question


```{r}

temp72 <- airquality[airquality$Temp == "72", ]

temp72_2 <- airquality %>% filter(Temp == "72")

```

#### Question 6

* You may have noticed when working with the `airqulity` data that some values show as `NA`
 * `NA` stands for not available, or missing values.
* A major part of data wrangling consists of cleaning missing values by either:
  * Dropping the lines that have missing values
   * Sometimes we can drop the column with missing values if the column is made of predominantly missing values
  * Imputing the missing values, which uses educated guesses (or more complex algorithms) to fill the missing values
  
* Find and remove all rows that are missing values for the `Solar.R` or `Ozone` variables
* Save the cleaned data to a new data frame called airquality_no_na
  * How many lines have been removed?


```{r}
airquality_no_na <- airquality %>%
  filter(Solar.R != "NA") %>%
  filter(Ozone != "NA")
```
##### 42 lines were removed

#### Question 7
* Let's use a different strategy and impute the missing value.
  * replace the missing values for Solar.R using that month's average.
  * Example:
    * The missing value for line 6 should be replaced with the average for month 5.
    * The missing value for line 97 should be replaced with the average for month 8.

```{r}
avg_by_month <- airquality %>%
  group_by(Month) %>%
  summarize(Average_Solar = mean(Solar.R, na.rm = TRUE), Average_Ozone = mean(Ozone, na.rm = TRUE))

```

```{r}
result_airquality <- airquality %>%
  left_join(avg_by_month, by = "Month") %>%
  mutate(Solar.R = ifelse(is.na(Solar.R), Average_Solar, Solar.R)) %>%
  select(-Average_Solar) %>%
  mutate(Ozone = ifelse(is.na(Ozone), Average_Ozone, Ozone)) %>%
  select(-Average_Ozone)
```

